An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-19 paper.tex
Grammar.

To show the effects of the treadmill dynamics and give an idea of the frequency
content of the actual perturbations, spectral density plots were created
by averaging a spectrogram of twenty second Hamming window, shown
in Figure~\ref{fig:freq_analysis}. For all speeds, the frequency content of the
commanded and measured time series show similarity below 4~\si{\hertz} and
attenuation in the measured spectral density above 4~\si{\hertz}.
%
\begin{figure}
  \centering
  \includegraphics{figures/frequency_analysis.pdf}
  \caption{Frequency spectrum of the treadmill belt velocity input signal
    (purple) and the recorded output velocity (blue) for average belt speeds of
    0.8, 1.2, and 1.6 m/s, respectively}
  \label{fig:freq_analysis}
\end{figure}

>>>>

To show the effects of the treadmill dynamics and give an idea of the frequency
content of the actual perturbations, spectral density plots were created
by averaging a spectrogram of a twenty second Hamming window, shown
in Figure~\ref{fig:freq_analysis}. For all speeds, the frequency content of the
commanded and measured time series show similarity below 4~\si{\hertz} and
attenuation in the measured spectral density above 4~\si{\hertz}.
%
\begin{figure}
  \centering
  \includegraphics{figures/frequency_analysis.pdf}
  \caption{Frequency spectrum of the treadmill belt velocity input signal
    (purple) and the recorded output velocity (blue) for average belt speeds of
    0.8, 1.2, and 1.6 m/s, respectively}
  \label{fig:freq_analysis}
\end{figure}
